\sectionTitle{Main Projects}{\faLaptop}

\begin{projects}
    \project
 	{Software Product Development}{March 2023 - Now}{}
 	{Development of a software product with a very complex architecture that aims to modernize old software systems and improve user experience.} 
 	{Java, Quarkus, Jira, Confluence}
    \project
 	{Data Platform development and management}{June 2022 - March 2023}{}
 	{This project consists in building a Data Platform for a customer using Azure's resources. The Data Platform uses an orchestrator to ingest data coming from different sources in a data lake. Data is manipulated and memorized using different levels of refinement. The goal is to visualize high refined data in dashboards suitable for business.} 
 	{Spark, Databricks, Azure, Terraform}
	\project
	{Secure Messaging}{May 2021 - June 2021}
	{\github{https://github.com/thorongil05/secure-messaging}{repository}
	\website{https://github.com/seraogianluca/secure-messaging/wiki}{Wiki}}
	{Messaging application with a console interface which uses OpenSSL to ensure confidentiality, integrity and authentication to the messages.}
	{C++ , C, OpenSSL,Cybersecurity}
 	\project
 	{Convolutional Neural Network for Medical Imaging Analysis}{February 2021}
 	{\github{https://github.com/thorongil05/Convolutional-Neural-Network-for-Medical-Imaging-Analysis}{repository}}
 	{Group project for the exam of Computational  Intelligence and Deep Learning. The goal is to classify the images of CBIS DDSMn dataset to make a breast cancer abnormalities diagnosis.} 
 	{Colab, TensorFlow, Keras}

    \project
 	{K-Means with MapReduce}{July 2020}
 	{\github{https://github.com/thorongil05/k-means-mapreduce.git}{repository}}
 	{Group project for the Cloud Computing exam.
 	The goal is to implement the \textit{K-Means} clustering algorithm in a distributed manner, exploiting \textit{map-reduce} paradigm.} 
 	{Hadoop, Spark, MapReduce}
\end{projects}